\vspace{.5cm} \textcolor{white} {Spin Canonical Rings of Log Stacky Curves}

### 2015-08-29 poster-curves/spin-canonical-poster.tex
added posters

%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass{amsart}

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}

@@

\theoremstyle{plain}
  \newtheorem{thm}{Theorem}[section]
  \newtheorem{prop}[thm]{Proposition}
  \newtheorem{lem}[thm]{Lemma}
  \newtheorem{cor}[thm]{Corollary}
	\newtheorem{question}[thm]{Question}

@@

\numberwithin{equation}{section}

@@

\newcommand{\PSL}{\operatorname{PSL}}

\renewcommand{\arraystretch}{1.2}

\makeatletter
\newcommand{\customlabel}[2]{%
   \protected@write \@auxout {}{\string \newlabel {#1}{{#2}{\thepage}{#2}{#1}{}} }%
   \hypertarget{#1}{#2}
}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Spin canonical rings of log stacky curves}

\author{Aaron Landesman}
\address[Aaron Landesman]{Department of Mathematics, Harvard University}
\email{aaronlandesman@college.harvard.edu}

\author{Peter Ruhm}
\address[Peter Ruhm]{Department of Mathematics, Stanford University}
\email{pruhm@stanford.edu}

\author{Robin Zhang}
\address[Robin Zhang]{Department of Mathematics, Stanford University}
\email{robinz16@stanford.edu}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
 	Consider modular forms arising from a finite-area quotient of the
	upper-half plane by a Fuchsian group. By the classical results of
	Kodaira--Spencer, this ring of modular forms may be viewed as the
	log spin canonical ring of a stacky curve. In this paper, we
	tightly bound the degrees of minimal generators and relations of
	log spin canonical rings. As a consequence, we obtain a tight bound
	on the degrees of minimal generators and relations for rings of
	modular forms of arbitrary integral weight.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has
finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
One of the best ways to describe the ring $M(\Gamma)$ is to write
down a presentation.
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
The main theorem of this work extends their result to all Fuchsian
groups $\Gamma$.

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann surface over $\BC$. 
Although $\Gamma \backslash \BH$ may be non-compact, we can form a
compact Riemann surface $\Gamma \backslash \BH^*$ by adding in
cusps (with associated divisor of cusps $\Delta$).

In order to find generators and relations for $M(\Gamma)$, we
translate the seemingly analytic question of understanding the ring
of modular forms into the algebraic category, using a
generalization of the GAGA principle.
As shown by Voight and Zureick-Brown \cite[Proposition 6.1.5]
{vzb:stacky}, there is an equivalence of categories between orbifold
curves and log stacky curves over $\BC$. For the remainder
of the paper, we will work in the algebraic category.

@@

Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
Petri's theorem in the direction of stacky curves equipped with
log spin canonical divisors. For a stacky curve $\sx$ with coarse space $X$ and
stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$, we define

\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
Then, a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ is a {\bf log spin canonical divisor}, meaning $2\halfcan \sim K_X +
\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
study in this paper is the {\bf log spin canonical ring} of $(\sx,
\Delta, \halfcan),$ defined as
\begin{align*}
	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor).
\end{align*}

\noindent
A brief overview of stacky curves, log divisors, and log spin
canonical rings is given in Subsection
~\ref{ssec:stacky-background}.

Our main theorem is to bound the degrees of generators and
relations of a log spin canonical ring. Let $\sx$ be a stacky curve
with signature $\sigma := (g; e_1, \ldots, e_r; \delta)$. The
application of O'Dorney's work \cite[Chapter 5]{dorney:canonical}
to log spin canonical rings gives a weak bound in the case $g = 0$
in terms of the least common multiples of the $e_i$'s. In their
treatment of log spin canonical rings, Voight and Zureick-Brown
\cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
\cdot \max(e_1, \ldots, e_r)$ and relation degrees by $12 \cdot \max
 (e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
bounds we deduce differ from those stated in Voight and
Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2
because their grading convention differs from ours by a factor of 2.

These bounds are far from tight and do not collectively
cover all cases in all genera. The main theorem of this paper
gives significantly tighter bounds for the log spin canonical ring
of any log spin curve.

@@

Then the log spin canonical ring is generated as a $\Bk$-algebra by 
elements of degree at most $e := \max(5, e_1, \ldots, e_r)$ with
relations generated in degrees at most $2e$,
so long as $\sigma$ does not lie in a finite list of exceptional
cases, as given in Table ~\ref{table:g-1-exceptional} for
signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
signatures with $g = 0$.
\end{thm}

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds with $\Delta$ replaced by an arbitrary effective divisor of the coarse space.
 Furthermore, one may relax the assumption that $\Bk$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
\end{rem}

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.

\begin{rem}
\label{rem:explicit-generators}
In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
of the genus one and genus zero cases of our main theorem also yield explicit systems
of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
Furthermore, our proof of the genus $g \geq 2$ case provides
an inductive procedure for explicitly determining the generators
and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.  Many
explicit systems of generators and relations for curves of genus $2
\leq g \leq 15$ are detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}

\begin{rem}
The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
In almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$. For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
\end{rem}

Combining the main theorem of this paper, Theorem ~\ref{thm:main} with the main theorem from Voight and Zureick-Brown ~\cite
[Theorem 1.4]{vzb:stacky} and a minor Lemma \cite[Lemma 10.2.1]{vzb:stacky}
we have the following application to
rings of modular forms.

\begin{cor}
\label{cor:main-mod-forms}
Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
associated to $\Gamma \backslash \BH$ with signature $\sigma
= (g; e_1, \ldots, e_r; \delta)$.

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $6 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $12 \cdot \max(3, e_1, \ldots, e_r)$.

If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
e_r)$ so long as $\sigma$ does not lie in a finite list of
exceptional cases which are listed and described in Table
~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
\end{cor}

\begin{rem}
\label{rem:gen-at-most-three}
If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$. When $g \geq 2$, we see that this is true because $\dim_\Bk H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$. When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}. Hence, there is an odd weight modular form in weight $3$ in general. A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
\end{rem}

\begin{example}
\label{eg:congruence-bounds}
In this example, we deduce bounds on the weight of generators and relations of the ring of modular forms associated to any congruence subgroup $\Gamma \subset SL_2(\BZ)$. Since
the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer
order 1, 2 and 3, and has at least one cusp, the
action of $\Gamma$ on $\BH$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.

If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4 and Theorem 9.3.1]{vzb:stacky}. Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.

If $\Gamma$ has some nonzero odd weight modular form, then it must 
have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
generated in degree at most $5$ with relations in degree at most $10$. Furthermore, it is not difficult to show that $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}. Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.
\end{example}

\begin{rem}
\label{rem:factor-two}
In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively. Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two. Our grading convention for log spin canonical rings uses weight $k$ for the degree whereas Voight and Zureick-Brown $d = 2k$ for degree.
\end{rem}

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:main}. The idea of the
proof will be to induct first on the number of stacky points and then on the stabilizer order of those points.  To this end, we first review important background in
Section ~\ref{sec:background}; providing essential examples in Section \ref{sec:examples}; develop various inductive
tools in Section ~\ref{sec:induction}; and prove Theorem ~\ref{thm:main} in genus $g\ge 2$, genus $g=1$, and genus $g=0$ in Sections ~\ref{sec:g-high},
~\ref{sec:g-1}, and ~\ref{sec:g-0} respectively.  
Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background}
\label{sec:background}
Here we collect various definitions and notation that will be
used throughout the paper. Many of the conventions come from existing
literature. For basic references on the statements and definitions
used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
Saint-Donat \cite{saint-donat:proj}, Arbarello--Cornalba--Griffiths--Harris 
\cite[Section III.2]
{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
Chapter 5]{vzb:stacky}.

For the remainder of this paper, fix an algebraically closed field $\Bk$.
This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closure.

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
We begin by setting up the notation for stacky curves and canonical rings. Wherever possible, we opt for a more elementary scheme-theoretic approach, instead of a stack-theoretic one. See Remark ~\ref{rem:stack-formalism} for more details.

\begin{defn}
\label{defn:stacky-curve}
A \textbf{stacky curve} $\sx$ over an algebraically closed field $\Bk$ is the datum of a smooth proper integral scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
\end{defn}

\begin{rem}
\label{rem:stack-formalism}
Stacky curves may be formally defined in the language of stacks, as
is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
Behrend and Noohi \cite{behrend-noohi:uniformization}.

The results of this paper can be easily phrased in terms of the language of stacks. If one works over an arbitrary field $\Bk$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.~ the residue field of each
of the stacky points is separable.

With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
of schemes.
\end{rem}

\begin{defn}
\label{defn:div-ex}
Let $\sx$ be a stacky curve over $\Bk$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
Then, we notate
\[
	\di \sx := \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

We can equip stacky curves with a log divisor $\Delta$ that is a 
sum of distinct points each with trivial stabilizer. 
A divisor
$\Delta$ of this form is called a \textbf{log divisor}. We use
$\delta := \deg \Delta$ to refer to the degree of the log divisor.
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.

\begin{defn}
\label{defn:divisor-floor}
If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
\lfloor \alpha_i \rfloor P_i$.
\end{defn}

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curve} and the study of their
canonical rings is the main focus of the work by Voight and 
Zureick-Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. Throughout the paper, we use
the notation $\halfcan_X := \lfloor L \rfloor.$ to refer to the log spin
canonical divisor (also known as the half-canonical divisor, 
semi-canonical divisor, or theta characteristic) associated to the
coarse space $X$ of $\sx.$  (i.e.~ $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). 
We define $H^0$ of a stacky divisor as follows.

\begin{defn}
\label{defn:h0-stacky}
Recall the standard notation for the line bundle $\sco(D)$ on an integral normal scheme $X$ associated to a divisor $D \in \di X$:
\[
	\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \} \cup \{0\}.
\]

\noindent
Let $\sx$ be a stacky curve with coarse space $X$.
If $D \in \di \sx$ is a Weil divisor, then we define
\begin{align*}
	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
\end{align*}
If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
graded component of $R$.

\end{defn}

\begin{rem}
Although Definition ~\ref{defn:h0-stacky} may seem fairly ad hoc, it is naturally motivated in the context of stacks. See Voight and Zureick-Brown \cite[Lemma 5.4.7]{vzb:stacky} for a proof that Definition ~\ref{defn:h0-stacky} is equivalent to the stack-theoretic description.
\end{rem}

\begin{defn}
\label{defn:order-sup}
Let $D \in \di \sx.$ If $z \neq 0$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

\begin{defn}
\label{defn:log-spin-canonical-ring}
The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
\[
	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
\]
\end{defn}

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
represent $R(\sx, \Delta, \halfcan)$.

\begin{rem}
\label{rem:odd-denom}
Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that $\halfcan$ is of the form
\[
	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i Q_i
\]

\noindent
where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
that $\halfcan \in \di \sx$: 
if some $e_i$ were even,
then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
\end{rem}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
\rfloor = \deg \Delta + 2(g-1).$
In particular, we shall often use $\deg \Delta \neq 1$.
\end{rem}

\ssec{Saturation}
We define the notion of the saturation of a divisor, as can be
found in Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
The classification of the saturations of log spin canonical
divisors are used in the proof of the main theorem and the various
lemmas in Section ~\ref{sec:induction}.

\begin{defn}
Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
is the monoid
\[
	\Eff(D) := \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
\]
\end{defn}

\begin{defn}
\label{defn:sat}
The \textbf{saturation of a monoid} $M \subseteq \BZ_{\geq 0}$,
denoted $\sat(M)$, is the smallest integer $s$ such that $M
\supseteq \BZ_{\geq s}$, if such an integer exists.
\end{defn}

\begin{rem}
For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the
\textbf{saturation of a divisor} $D$. For examples,
see Subsection ~\ref{ssec:g-0-saturation}.
\end{rem}

\ssec{Monomial Ordering}
\label{ssec:monomial-order}
Here we give a brief overview of the three monomial orderings
that we use. For further reference on monomial orderings,
initial ideals, and Gr\"{o}bner bases, see Eisenbud
\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--O'Shea
\cite[Chapter 2]{cls:ideals-varieties-algorithms}.

\begin{defn}
\label{defn:monomial-degree}
Let $\Bk[x_1$, $\ldots$, $x_n]$ be a graded polynomial
ring with $\deg x_i = k_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
\Bk[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
we define the {\bf degree} of $\alpha$ to be
\[
	\deg \alpha := \sum_{i = 1}^{n} k_i f_i.
\]
\end{defn}

\begin{defn}
\label{defn:grevlex}
The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
monomials in $\Bk[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
\succ_{\text{grevlex}} \beta$ if either

\begin{equation}
	\deg \alpha = \sum_{i = 1}^{n} k_i f_i  > \sum_{i = 1}^{n} k_i f_i' = \deg \beta
\end{equation}
or
\begin{equation}
\label{eqn:grevlex-tie}
	\deg \alpha = \deg \beta \text{ and }	f_i < f_i' \text{ for
	the	largest } i \text{ such that } f_i \neq f_i'.
\end{equation}
\end{defn}

\begin{rem}
Note that the ordering of the variables matters in Equation
~\ref{eqn:grevlex-tie}.
\end{rem}

Our inductive arguments in Section ~\ref{sec:induction} will
usually have an inclusion $R \supseteq R'$ of log spin canonical
rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
natural to consider term orders which treat these sets of variables
separately.

\begin{defn}
\label{defn:block-order}
The \textbf{block term order} is defined as follows. Let $\Bk[y_{1}, \ldots, y_{m}]$ and $\Bk[x_{1}, \ldots,
x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = k_i.$ Further assume we are given existing term
orders $\prec_y$ and $\prec_x$. Let $\alpha :=
\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $\Bk[y_{1},
\ldots, y_{m}] \otimes$ $\Bk[x_{1}, \ldots, x_{n}]$.
Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
part of $\alpha$ in $\Bk[y_{1}, \ldots, y_{m}]$ and
likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.

>>>>

\documentclass[landscape, a0, largefonts]{sciposter}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{array}
\usepackage{ytableau}
\usepackage{verbatim}
\usepackage[vcentermath]{youngtab}
\newlabel{fig2:a}{{I(a)}{1}}
\newlabel{fig2:b}{{I(b)}{1}}
\newlabel{fig:i}{{II(c)}{1}}
\newlabel{fig:ii}{{II(d)}{1}}
\newlabel{fig:iii}{{II(e)}{1}}
\newlabel{fig3:c}{{III(f)}{1}}
\newlabel{fig3:d}{{III(g)}{1}}
\newlabel{fig4:i}{{IV(h)}{1}}
\newlabel{fig4:ii}{{IV(i)}{1}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\row}{\mathfrak{row}}
\newcommand{\oh}{\operatorname{outerhook}}
\newcommand{\col}{\mathfrak{col}}
\newcommand{\lis}{\mathfrak{lis}}
\newcommand{\lds}{\mathfrak{lds}}
\newcommand{\sss}{\scriptstyle} %% for tableaux
\newcommand{\swap}{\operatorname{swap}}
\newcommand{\jdt}{\operatorname{jdt}}
\newcommand{\std}{\operatorname{std}}
%\usepackage{fancybullets}
%\usepackage{other packages you may want to use}

\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}

@@

\theoremstyle{plain}
  \newtheorem{thm}{Theorem}
  \newtheorem{prop}[thm]{Proposition}
  \newtheorem{lem}[thm]{Lemma}
  \newtheorem{cor}[thm]{Corollary}
	\newtheorem{question}[thm]{Question}

@@

@@

%\definecolor{BoxCol}{cmyk}{0.9,0.9,0.9}
% uncomment for grey background to \section boxes 
% for use with default option boxedsections

\definecolor{mainCol}{rgb}{1,1,1} %background
\definecolor{BoxCol}{rgb}{.1,.1,.3} 
\definecolor{TextCol}{rgb}{0.2,0.5,0.5}
\definecolor{SectionCol}{rgb}{1,1,1} %section header
\definecolor{ShadeCol}{rgb}{.9,.95,.9}
\definecolor{lightpurple}{rgb}{.1,.1,.3} %title box shade
\definecolor{navy}{rgb}{0.2,0.3,0.5} 	
\definecolor{white}{rgb}{1,1,1}
\def\NN{{\mathbb{N}}}
\def\RR{{\mathbb{R}}}
\newcommand{\Z}{\mathbb{Z}} 
%\definecolor{BoxCol}{rgb}{0.9,0.9,1}
% uncomment for light blue background to \section boxes 
% for use with default option boxedsections

%\definecolor{SectionCol}{rgb}{0,0,0.5}
% uncomment for dark blue \section text

\title{\vspace{.5cm} \textcolor{white} {Spin Canonical Rings of Log Stacky Curves}}

% Note: only give author names, not institute
\author{\textcolor{white}{Aaron Landesman, Peter Ruhm, and Robin Zhang}}

%\email[Aaron Landesman]{aaronlandesman@college.harvard.edu}

% insert correct institute name
\institute{\vspace{-.25cm} \textcolor{white}{Harvard University, Stanford University, Stanford University}}

%\date is unused by the current \maketitle

%\leftlogo[0.9]{nsf_logo.png}  % defines logo to left of title (with scale factor)
%\rightlogo[1.0]{umnlogo.png} % same but on right

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%*** facultative: where the poster was presented (appears as a left footer):
  %\conference{LSU Discover Research Day, 2014, Baton Rouge, LA}

%*** print the poster header defined above: title, authors, affiliations:
 \fbox{\colorbox{lightpurple}{\maketitle}}
\\
\\
  \begin{multicols}{3}
	  \begin{tcolorbox}
	  \section*{Abstract}

 	Consider modular forms arising from a finite-area quotient of the
	upper-half plane by a Fuchsian group. By the classical results of
	Kodaira--Spencer, this ring of modular forms may be viewed as the
	log spin canonical ring of a stacky curve. In this paper, we
	tightly bound the degrees of minimal generators and relations of
	log spin canonical rings. As a consequence, we obtain a tight bound
	on the degrees of minimal generators and relations for rings of
	modular forms of arbitrary integral weight.
\end{tcolorbox}

  \section*{\textsc{Notation}}
  \begin{align*}
	  \Bbbk & & \text{Perfect Field} \\
	  \sx & & \text{Stacky Curve} \\
	  X & & \text{Coarse Space} \\
	  g & & \text{Genus} \\
	  \Delta & & \text{Log Divisor} \\
	  \delta & & \text{Degree of Log Divisor} \\
	  P_1, \ldots, P_r \in \text{Spec } X & & \text{Stacky Points} \\
	  e_1, \ldots, e_r \in \BZ_{\geq 2}  & & \text{Stacky Orders} \\
	  (g; e_1,\ldots, e_r; \delta) & & \text{Signature} \\
	\lfloor \sum_{i=1}^n \alpha_i P_i \rfloor := \sum_{i=1} \lfloor \alpha_i\rfloor P_i & & \text{Floor of a Stacky Divisor} \\
	K_X & & \text{Canonical Divisor of Coarse Space} \\
	K_\sx := K_X + \sum_{i=1}^n \frac{e_i-1}{e_i} P_i & & \text{Canonical Divisor of Stacky Curve} \\
	(\sx, \Delta, L), 2L \sim K_\sx + \Delta & & \text{Log Spin Curve} \\
	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor) & & \text{Log Spin Canonical Ring}
  \end{align*}

  \section*{\textsc{Introduction}}

@@

Our main theorem is to bound the degrees of generators and
relations of a log spin canonical ring. In 
~\cite[Theorem 1.4]{vzb:stacky}, Voight and Zureick-Brown tightly
bounde the degree of generation and
relations of a log spin canonical ring.

  \section*{\textsc{Main Result}}

@@

Then the log spin canonical ring is generated as a $\Bk$-algebra by 
elements of degree at most $e := \max(5, e_1, \ldots, e_r)$ with
relations generated in degrees at most $2e$,
so long as $\sigma$ does not lie in a finite list of exceptional
cases, as given in Table ~\ref{table:g-1-exceptional} for
signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
signatures with $g = 0$.
\end{thm}
{\bf Proof idea:} First, check this holds when $\Delta \in \di X$,
either by hand in $g = 0, 1$ or by 
\cite[$\mathsection$ 6]{milnor:fractional-weight} when $g \geq 2$.
Then, inductively add in fractional points, showing that if
it holds for a given divisor $\Delta$ it holds for
$\Delta + \frac{e-1}{2e}P$.

\begin{table}
\captionsetup{type=figure}
\begin{center}
\begin{tabular}
	{| c || c | c | c |}
	\hline
	Signature $\sigma$ & Generator Degrees & Degrees of Relations & $e$ \\
	\hline
	\hline
